Binary companions of red clump stars

### 2017-03-02 paper/main.tex
typos and explanation

If we want to use a spectroscopic survey to responsibly measure the
binary-star population---that is, if we want to get (say) the mass,
mass ratio, and period distribution of binary star systems---we face
(at least) two challenges.
The first is how, given a small number of observations of a primary
star (in the case, say, of SB1 stars), do we reliably obtain posterior
information about the binary-system properties?
After all, if there are only a few radial-velocity measurements made
per star, any observed radial-velocity values will be consistent with
many different combinations of period and amplitude (not to mention
eccentricity and argument of perihelion) for the primary orbit.
In general, the likelihood function, and the posterior pdf under any
reasonable prior pdf, will be highly multimodal in these kinds of
problems, and many of the modes will have comparable integrated
probability density.
We have solved this problem previously, though with limitations (to be
discussed more below), with \thejoker\ (CITE).
\thejoker\ is a Simple Monte Carlo rejection sampler that is
computationally expensive but probabilistically righeous: It delivers
independent (zero-auto-correlations) posterior pdf samples for
single-companion binary model parameters, given any number of
radial-velocity measurements.

The second challenge is how, given all these noisy, multi-modal
posterior pdfs overy binary-system properties, many of which will
permit a wide range of qualitatively different system properties, and
many of which will be consistent with no companion at all, can we
constrain parameters of a model of the full binary-system population?
No histogram of best-fit values, nor stack of multi-modal posteriors,
would be anything like a good estimate of the true population
distribution.
We have also solved this problem previously, though in the exoplanet
domain, with hierarchical probabilistic models based on importance
sampling (CITE DFM, and also HOGG).
These hierarchical models derive posterior estimates of the population
parameters that accurately describe the population, given the noisy
information about the individual systems, provided that the noise
model is accurate---that is, provided that the likelihood functions
used in the individual-system inferences are themselves accurate.

Here we mash up these two solutions to these two challenges.
We deliver a catalog of binary-star systems with \RC\ primaries, and also
posterior information about the full population statistics.

>>>>

If we want to use a spectroscopic survey to responsibly measure the
binary-star population---that is, if we want to get (say) the mass,
mass ratio, and period distribution of binary star systems---we face
(at least) two challenges.
The first is how, given a small number of observations of a primary
star (a single-lined spectroscopic binary star), do we reliably obtain posterior
information about the binary-system properties?
After all, if there are only a few radial-velocity measurements made
per star, any observed radial-velocity values will be consistent with
many different combinations of period and amplitude (not to mention
eccentricity and argument of perihelion) for the primary orbit.
In general, the likelihood function, and the posterior pdf under any
reasonable prior pdf, will be highly multimodal in these kinds of
problems, and many of the modes will have comparable integrated
probability density.
We have solved this problem previously, though with limitations (to be
discussed more below), with \thejoker\ (CITE).
\thejoker\ is a Simple Monte Carlo rejection sampler that is
computationally expensive but probabilistically righteous: It delivers
independent (zero-auto-correlations) posterior pdf samples for
single-companion binary model parameters, given any number of
radial-velocity measurements.

The second challenge is how, given all these noisy, multi-modal
posterior pdfs over binary-system properties, many of which will
permit a wide range of qualitatively different system properties, and
many of which will be consistent with no companion at all, can we
constrain parameters of a model of the full binary-system population?
No histogram of best-fit values, nor stack of multi-modal posteriors,
would be anything like a good estimate of the true population
distribution.
We have also solved this problem previously, though in the exoplanet
domain, with hierarchical probabilistic models based on importance
sampling (CITE DFM, and also HOGG).
These hierarchical models derive posterior estimates of the population
parameters that accurately describe the population, given the noisy
information about the individual systems, provided that the noise
model is accurate---that is, provided that the likelihood functions
used in the individual-system inferences are themselves accurate.

Here we mash up these two solutions to these two challenges.
We deliver a catalog of binary-star systems with \RC\ primaries, and also
posterior information about the full population statistics, for at least
a toy model of that full population.
We use all the data---even the non-detections, marginal detections, and
badly multi-modal posterior pdfs---when we infer the population model;
that is, we don't arbitrarily cut to a catalog of ``clean'' binaries.
